My title

### 2024-03-13 paper/paper.qmd
Model new connections and relations

deaths_data <- read.csv(here("data/analysis_data/cleaned_file.csv"))
air_quality_data <- read.csv(here("data/analysis_data/cleaned_air_data.csv"))
```

@@

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

causes_model <-
  readRDS(file = here::here("models/causes_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = causes_model
  ),
  #statistic = "mad",
  fmt = 2
)
```

@@

# Create the posterior predictive check plot
pp_plot <- pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

# Create the posterior vs prior plot
posterior_plot <- posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

>>>>

deaths_data <- read.csv(here("data/analysis_data/cleaned_file.csv"))
air_quality_data <- read.csv(here("data/analysis_data/cleaned_air_data.csv"))
data <- read.csv(here("data/analysis_data/cleaned_chart_data.csv"))
data_peak <- read.csv(here("data/analysis_data/cleaned_peak_data.csv"))
```

@@

# Plot the regression graph
ggplot(data, aes(x = total_deaths, y = provincial_average)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line without confidence interval
  labs(x = "Total Deaths", y = "Provincial Average", title = "Regression Graph") +
  theme_minimal()

# Plot the regression graph
ggplot(data_peak, aes(x = total_deaths, y = provincial_average)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line without confidence interval
  labs(x = "Total Deaths", y = "Provincial Average", title = "Regression Graph") +
  theme_minimal()

# Plot the regression graph
ggplot(data_peak, aes(x = provincial_average, y = total_deaths)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line without confidence interval
  labs(x = "Provincial Average", y = "Total Deaths", title = "Regression Graph") +
  theme_minimal()

# Plot the regression graph
ggplot(data, aes(x = provincial_average, y = total_deaths)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line without confidence interval
  labs(x = "Provincial Average", y = "Total Deaths", title = "Regression Graph") +
  theme_minimal()

```

@@

causes_model <-
  readRDS(file = here::here("models/causes_model.rds"))

p_average_model <-
  readRDS(file = here::here("models/p_average_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = causes_model
  ),
  #statistic = "mad",
  fmt = 2
)

modelsummary::modelsummary(
  list(
    "First model" = p_average_model
  ),
  #statistic = "mad",
  fmt = 2
)
```

@@

pp_check(p_average_model) +
  theme(legend.position = "bottom")

# Create the posterior predictive check plot with the specified theme
pp_plot <- pp_check(p_average_model, theme = theme_classic()) +
  theme(legend.position = "bottom")

# Create the posterior vs prior plot with the specified theme
posterior_plot <- posterior_vs_prior(p_average_model, theme = theme_minimal()) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```
